---
title: "THERESA_M6"
author: "Theresa Agnes Virnauli Sinaga"
date: "2023-03-17"
output: html_document
---
1. Misal ▁X menyatakan rerata sampel acak berukuran 100 dari sebaran χ^2 (50). Tampilkan histogram melalui CLT dengan pengambilan sampel 50, 500, dan 5000
```{r}
# import random number (data) dan set
set.seed(123)
#mencari mean pada interval 50, 500, 5000 data dengan perulangan dan disimpan pada masing- masing variabel
k_50 = 50
n_50 = c()
for (i in 1:k_50){
 n_50[i] = mean(rchisq(n=100,df=50))
}
k_500 = 500
n_500 = c()
for (i in 1:k_500){
 n_500[i] = mean(rchisq(n=100,df=50))
}
k_5000 = 5000
n_5000 = c()
for (i in 1:k_5000){
 n_5000[i] = mean(rchisq(n=100,df=50))
}
# membuat histogram
par(mfrow = c(1,3))
hist(n_50, col = "red", main = "n = 50", xlab = "Rerata Sampel Acak 50 Pengambilan")
abline(v = mean(n_50), col = 'black')
hist(n_500, col = "green", main = "n = 500", xlab = "Rerata Sampel Acak 500 Pengambilan")
abline(v = mean(n_500), col = 'black')
hist(n_5000, col = "blue", main = "n = 5000", xlab = "Rerata Sampel Acak 5000 Pengambilan")
abline(v = mean(n_5000), col = 'black')
```

2. Misal ▁X menyatakan rerata sampel acak berukuran 1000 dari sebaran Exp(0.25). Tampilkan histogram melalui CLT dengan pengambilan sampel 20, 200, dan 2000
```{r}
# import random number (data) dan set
set.seed(123)
#mencari mean pada interval 50, 500, 5000 data dengan perulangan dan disimpan pada masing- masing variabel
k_20 = 20
n_20 = c()
for (i in 1:k_20){
 n_20[i] = mean(rexp(n=1000,rate=0.25))
}
k_200 = 200
n_200 = c()
for (i in 1:k_200){
 n_200[i] = mean(rexp(n=1000,rate=0.25))
}
k_2000 = 2000
n_2000 = c()
for (i in 1:k_2000){
 n_2000[i] = mean(rexp(n=1000,rate=0.25))
}
# membuat histogram
par(mfrow = c(1,3))
hist(n_20, col = "red", main = "n = 20", xlab = "Rerata Sampel Acak 50 Pengambilan")
abline(v = mean(n_20), col = 'black')
hist(n_200, col = "green", main = "n = 200", xlab = "Rerata Sampel Acak 500 Pengambilan")
abline(v = mean(n_200), col = 'black')
hist(n_2000, col = "blue", main = "n = 2000", xlab = "Rerata Sampel Acak 5000 Pengambilan")
abline(v = mean(n_2000), col = 'black')
```

3. In a recent New York Times article, it was reported that light trucks, which include SUV’s, pick-up trucks and minivans, accounted for 40% of all personal vehicles on the road in 2023. Assume the rest are cars. Of every 200,000 car accidents, 40 involve a fatality; of every 200,000 light truck accidents, 50 involve a fatality. If a fatal accident is chosen at random, what is the probability the accident involved a light truck?

```{r}
p_light_trucks = 0.4
p_car = 1 - p_light_trucks #assume the rest are the cars
p_light_trucks_fatality = (50/200000)
p_car_fatality = (40/200000)
#the probability the accident involved a light truck --> P(A) = n(A)/n(S)
nA = p_light_trucks_fatality*p_light_trucks
nS = (p_light_trucks_fatality*p_light_trucks) + (p_car*p_car_fatality)
PA = nA/nS
PA #result of probability the accident involved a light truck 
```

```{r}
p_virus = 14/10000
p_no_virus = 1 - p_virus
p_positive_virus = 0.995 #diket di soal
p_positive_no_virus = 0.1 #diket di soal
nA = p_virus*p_positive_virus
nS = ((p_virus*p_positive_virus) +(p_no_virus*p_positive_no_virus))
PA = nA/nS
PA #result of probability that a person actually has the virus given that the person is tested positive 
```